Supplementary Information

### 2020-06-03 doc/manuscript/MEE_manuscript.Rmd
update manuscript

First, $\Delta r$ typically declines with tree size in cored individuals, consistent with many previous observations from tree-ring records (DENDRO_REFS).

>>>>

On climate sensitivity:
- Climwin step is problematic when cliamte is rapdidly changing [ISSUE #25 in ForestGEO-climate-sensitivity ](https://github.com/EcoClimLab/ForestGEO-climate-sensitivity/issues/25).

On DBH:
First, $\Delta r$ typically declines with tree size in cored individuals, consistent with many previous observations from tree-ring records (DENDRO_REFS).
